---
title: "monthly-bldg-permit-report"
author: "Logan Williams"
date: "3/11/2021"
output: html_document
params:
#change EVERY month
  month: June
  year: 2021
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
#load dependencies
library(dplyr)        # data manipulation
library(readr)        #download csv
library(here)         #file path management
library(kableExtra)   #data tables

# spatial packages
library(tmap)         # map layouts
library(tmaptools)    # tools for handeling spatial
library(sf)           # spatial data tools

#other packages
library(RColorBrewer) # cynthia brewer color palettes
library(viridis)      # color palettes
library(knitr)
library(ggplot2)      # plot making
library(formattable)  # currency values
library(lubridate)    # manipulate date time data
library(officer)      # powerpoint manipulation
library(flextable)    # nice tables
library(customLayout) # custom powerpoint layout
library(rlang)        # check for empty values
library(tidyr)        # used to drop NA
library(docxtractr)   #convert pptx to pdf
library(gateway)      #get STL spatial boundaries
library(grid)
```

```{r, include=FALSE}
#load data
#setwd('/Users/loganbogenut/Documents/GitHub/stl-building-permits')

load(file = here::here("data", params$year, params$month, "clean-permit-data.rda"))
load(file = here::here("data", "basemap_tiles", "mapbox-tiles.rda"))
load(file = here::here("data", "basemap_tiles", "boundaries.rda"))
load(file = here::here("data", "basemap_tiles", "nbhd-boundaries.rda"))

#create powerpoint
report <- read_pptx()

bound <- gw_get_data("Neighborhoods", "sf") #get neighborhood boundaries
nbhd_num <- c("38", "39", "46", "47", "48", "49", "51", "53", "54", "58")
names <- c("Central West End", "Forest Park Southeast", "Skinker DeBaliviere", "DeBaliviere Place", "West End", "Visitation Park", "Academy", "Fountain Park", "Lewis Place", "Vandeventer")
use <- c("Industrial", "Residential", "Commercial")
```

#Function References

`lay_new` creates a custom layout. You use the `matrix` argument to specify the location of figures.

`lay_bind_row` combines custom layouts. In this instance, we are combining the title layout with the body layout for our powerpoint slide.

`phl_layout` transforms your custom layout to an officer PowerPoint slide.

`fp_text` creates a font style for an officer powerpoint slide.

`ftext` creates a formatted chunk of text, often referencing `fp_text` for formatting instructions.

`fpar` creates formatted paragraphs in Powerpoint. Used to concatenate `ftext` objects into a paragraph.

`block_list` combines several blocks, or `fpar` objects, into a single object. Used to create formatted paragraphs in Powerpoint.

`read_pptx` creates a powerpoint presentation. You can use a variety of functions to add content to the presentation once the object is created.

`add_slide` adds a powerpoint slide to an existing powerpoint object. Specify what kind of layout you want the slide to be.

`ph_with` adds content to an existing powerpoint slide. This function often follows the `add_slide` function. This function is used to add everything from tables, to titles to body paragraphs on your powerpoint slide.

`sprintf` creates a character vector containing a formatted combination of text and variable values. In this notebook it is used for summary notes where it references the paramaters as well as certain variable values.

`filter` is a dplyr function that is used to clean data. Specifically it is used to find rows/cases where a condition is true. If the condition is true then the values are kept, if not they are dropped.

`group_by` takes an existing tbl and converts it into a grouped tbl based on a specific variable.

`rename` does exactly what you think it does. It renames variables based on name.

`replace` replaces a certain value with another. It is used in this notebook to replace NAs with 0.

`add_row` adds a row to a dataframe. It is used to add rows to tables based on whether or not a specific crime was committed. So, if there were no arsons that month, the `add_row` function is used to add this crime with values of 0.

`arrange` sorts a variable in ascending order

`adorn_totals` adds a "totals" row or column to a data frame.

`colformat_num` formats numeric variables in a flextable. Specifically aimed at controlling the number of digits displayed.

`add_header_lines` adds a header to a flextable.

`autofit` is used to automatically adjust flextable height and width to fit the size of desired content.

`is_empty` checks if an object has a value or not. If the value is missing, then we use `add_row` to add the missing permit type.

`tm_shape` creates a tmap-element that draws polygons.

`tm_fill` fills map shapes based on what you want. You can either choose a fixed color or map create a color palette mapped to a variable.

`tm_borders` adds borders to a map shape

`tm_credits` adds map credits.

`tm_bubbles` creates bubbles. This is how we represent crime points on a map.

`tm_layout` specifies map layout. Used for controlling/creating map legend

`tmap_save` saves a tmap object.

`ggsave` saves a ggplot object.

`theme` is a ggplot function that allows you to control the non-data parts of your plot (i.e. title, labels, fonts, etc.)

`convert_to_pdf` uses libreOffice (another application) to convert the saved powerpoint into a PDF.

`ggplot` initializes a ggplot object. Can be used to specify the data frame and the plot aesthetics.

`geom_bar` creates a bar plot in a ggplot object

`geom_text` is used to place text in a ggplot object. It is used in this notebook to label the stacked bar chart values that are greater than a certain amount.

`coord_flip` flips the x and the y axis in ggplot.

`scale_colour_manual` used to assign specific color values to ggplot. This references the `cols` vector to make sure that symbology is consistent throughout the report.

`xlab` `ylab` creates axis labels in a ggplot object.

`unique` returns all unique values in a given vector. It is used in the `for` loop of this notebook to extract the neighborhood name in each iteration of the loop.

`comment` adds a comment to any R object. It is used in this notebook to add the neighborhood name to the basemap tiles. This helps the `for` loop run more efficiently.

`min` returns the minimum value in a vector.

`max` returns the maximum value in a vector.

`median` returns the median value of a vector.

`mean` returns the mean average of a vector.

`sum` returns the total sum of a vector

`currency` formats values as currency.

`is.infinite` checks if a value is infinite or not. It is used in the summary notes to identify whether a perentage change is infinite or not, i.e. dividing a number by 0.

`is.nan` is used to check if a value is NA or not. It is used in the summary notes to identify NA values, which are instances where mathematic operations cannot apply, i.e. when there are no building permits and ergo no values to perform such operations.

`percent` formats values as a percentage

`as.numeric` formats values as numberic.

`summarise` or `summarize` are used in conjunction with `group_by` to create an output that has one row for each group specified in the `summarise` function.

`set_header_lables` allows you to change column names in a flextable.

`st_as_sf` converts an object into a simple feature object.

`st_transform` transforms or converts the coordinates of a simple feature object.

`dollar_format` is used with ggplot to represent values in dollar format.

`st_write` writes a simple feature to a file or database.

`st_read` reads a simple feature from a file or databease.

`scale_y_continuous` is used to set y axis labels. Used with `dollar_format` in order to format y axis labels in dollar format.

`gw_get_data` is from the `Gateway` package which is specifically used for accessing St. Louis City data.

`merge` combines two datasets by a certain variable.

```{r, include=FALSE}
#import parcel data
st_read(here::here("data", "working-db", "parcels", "prcl.shp"),
        stringsAsFactors = FALSE) %>%
  st_transform(crs = 32615) -> prcl
```

```{r, include=FALSE}
#make sure both are numeric
data_month$HANDLE <- as.numeric(data_month$HANDLE)
prcl$HANDLE <- as.numeric(prcl$HANDLE)

#merge by handle
merge <- data_month%>%
  merge(prcl, by = "HANDLE")
```

```{r}
#create custom color palette for plots
cols <- c("Industrial" = "#e41a1c", "Residential" = "#377eb8", "Commercial" = "#4daf4a")

# summary note colors
reg24 <- fp_text(color = 'black', font.size = 24)
reg20 <- fp_text(color = 'black', font.size = 20)
boldline <- fp_text(color = "black", font.size = 28, bold = TRUE, underlined = TRUE)
bold <- fp_text(color = "black", font.size = 24, bold = TRUE)
```

```{r officer layout}
#create custom powerpoint layout
lay <- lay_new(matrix(1:2)) 
title <- lay_new(1, widths = 2, heights = 2)
layout <- lay_bind_row(title, lay, heights = c(1,6))
lay_show(layout)

offlayout <- phl_layout(layout,
    margins = c(0.25, 0.25, 0.25, 0.25),
    innerMargins = rep(0.15,4))

lay1 <- lay_new(matrix(1:4, nc = 2), widths = c(2,2), heights = c(2,1)) 
title1 <- lay_new(1, widths = 2, heights = 2)
layout1 <- lay_bind_row(title1, lay1, heights = c(1,6))
lay_show(layout1)

offlayout01 <- phl_layout(layout1,
    margins = c(0, 0, 0, 0),
    innerMargins = rep(0.15,4))
```

```{r}
# All Neighborhood Building Permit Map
merge_sf <- st_as_sf(merge)

bound%>%
filter(NHD_NUM %in% nbhd_num) -> bound_sub

#inset map
bound%>%
tm_shape()+
  tm_fill(col = "grey")+
  tm_borders(col = "white")+
  bound_sub%>%
  tm_shape()+
  tm_fill(col = "forestgreen")+
  tm_borders(col = "white") -> inset

bound_sub%>%
tm_shape()+
  tm_fill(col = "grey")+
  tm_borders(col = "white")+
  merge_sf%>%
  tm_shape() +
  tm_bubbles(size = .25,
               col = "new_use",
               palette = "Set1",
               title.col = "Building Permit Type") +
  tm_credits("Source: City of St. Louis", position = c("left", "BOTTOM"), size = .5) +
    tm_credits(paste("Date Created:", Sys.Date()), position = c("right", "BOTTOM"), size = .5)+
  tm_layout(
    main.title = paste("St. Louis Central Corridor West\nBuilding Permits -", params$month, params$year),
    main.title.position = "center",
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom"))-> map

tmap_save(map, insets_tm = inset, insets_vp = viewport(0.8, 0.75, width = 0.4, height = 0.4), file = here::here("results", params$year, params$month, "all_nbhds", "allbldg_map.jpeg"), width = 10.5, height = 5.9, units = "in")
```

```{r}
#title slide
report%>%
  add_slide(layout = "Title Slide", master = "Office Theme")%>%
  ph_with(value = "St. Louis Central Corridor West Building Permits", location = ph_location_type(type = "ctrTitle"))%>%
  ph_with(paste("Monthly Report:", params$month, params$year, sep = " "), location = ph_location_type(type = "subTitle"))%>%
  ph_with(value = "Washington University Medical Center", location = ph_location_type(type = "dt")) -> report

#add STL map reference
report%>%
add_slide()%>%
  ph_with(external_img(here::here("data", "neighborhood_pics", "spat_ref.png"), height = 5, width = 9),
          ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("St. Louis Neighborhood Spatial Reference", 
               location = ph_location_type(
                 type = "title") )-> report
```

### All Neighborhoods: Summary

```{r}
# Average cost by neighborhood for each `new_use`

ggplot(means, aes(x = nbhd_name, y = mean, fill = new_use)) +
  scale_colour_manual(
    values = cols,
    aesthetics = c("colour", "fill")
  ) +
  geom_bar(position = "dodge", stat="identity") +
  theme(plot.title = element_text(hjust = 0.5),
    axis.title.y = element_blank()) +
  ylab("Cost") +
  labs(fill = "New Use") +
  scale_y_continuous(labels = scales::dollar_format())+
  coord_flip()

ggsave(here::here("results", params$year, params$month, "all_nbhds", "allnbhd_plot.png"), 
       width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "all_nbhds", "allnbhd_plot.png"), width = 9, height = 5),
          location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("Neighborhood Summary: Average Building Permit Cost", 
               location = ph_location_type(
                 type = "title") )-> report

```

```{r, echo = FALSE}
#create summary tables for current month and past 6 months
data_month%>%
  group_by(nbhd_name)%>%
  summarize(mean = mean(EstProjectCost), count = n(), sum = sum(EstProjectCost))%>%
  dplyr::select(nbhd_name, mean, count, sum) -> table

names[!(names %in% table$nbhd_name)] -> missing_category
is_empty(missing_category) -> test

as.data.frame(table) -> table

if(test == FALSE) {
  add_row(table, nbhd_name = missing_category) -> table
}
table%>%
  replace(., is.na(.), 0)%>%
  arrange(., nbhd_name) -> table

  
month6%>%
  group_by(nbhd_name)%>%
  summarize(mean = mean(EstProjectCost), count = n(), sum = sum(EstProjectCost))%>%
  dplyr::select(nbhd_name, mean, count, sum) -> table1

names[!(names %in% table1$nbhd_name)] -> missing_category
is_empty(missing_category) -> test

as.data.frame(table1) -> table1

if(test == FALSE) {
  add_row(table1, nbhd_name = missing_category) -> table1
}
table1%>%
  replace(., is.na(.), 0)%>%
  arrange(., nbhd_name) -> table1
  
#make summary tables
  flextable(table)%>%
  colformat_num(., digits = 0)%>%
  colformat_num(., digits = 0, prefix = "$", j = c(2,4)) %>%
  autofit()%>%
  add_header_lines(values = paste(params$month, params$year, sep = " "))%>%
  set_header_labels(nbhd_name = "Neighborhood", 
    mean = "Average Cost", count = "# of Permits", sum = "Total Value of Permits")%>%
    height_all(height = .4, part = "all")-> flex
  
  flextable(table1)%>%
  colformat_num(., digits = 0)%>%
  colformat_num(., digits = 0, prefix = "$", j = c(2,4)) %>%
  autofit()%>%
  add_header_lines(values = "Last 6 Months")%>%
  set_header_labels(nbhd_name = "Neighborhood", 
    mean = "Average Cost", count = "# of Permits", sum = "Total Value of Permits")%>%
    height_all(height = .4, part = "all")-> flex01

# add powerpoint slide
report%>%
  add_slide()%>%
  ph_with("Neighborhood Summary", 
               location = ph_location_type(
                 type = "title"))%>%
  phl_with_flextable(olay = offlayout01, 2, flex)%>%
  phl_with_flextable(olay = offlayout01, 4, flex01) -> report
```

#Individual Neighborhood Summaries

```{r}
#create comments to use to filter and name outputs
comment(cwe_tiles) <- "38"
comment(fpse_tiles) <- "39"
comment(sdb_tiles) <- "46"
comment(dbp_tiles) <- "47"
comment(we_tiles) <- "48"
comment(vp_tiles) <- "49"
comment(ac_tiles) <- "51"
comment(fp_tiles) <- "53"
comment(lp_tiles) <- "54"
comment(vd_tiles) <- "58"

for (i in list(cwe_tiles, fpse_tiles, sdb_tiles, dbp_tiles, we_tiles, vp_tiles, ac_tiles, fp_tiles, lp_tiles, vd_tiles)) {
  num <- as.numeric(comment(i))
  if(num %in% data_month$Nbrhd){
  nbhd_pres <- filter(data_month, Nbrhd == num)
  neighborhood <- unique(nbhd_pres$nbhd_name)
abbr <- unique(nbhd_pres$abbr)

#create mean, median, range stats
mean <- mean(nbhd_pres$EstProjectCost)
mean <- currency(mean, digits = 0L)
if(is.nan(mean)){mean[is.nan(mean)] <- 0}
if(is.infinite(mean)){mean[is.infinite(mean)] <- 0}
median <- median(nbhd_pres$EstProjectCost)
median <- currency(median, digits = 0L)
if(is.nan(median)){median[is.nan(median)] <- 0}
if(is.infinite(median)){median[is.infinite(median)] <- 0}
min <- min(nbhd_pres$EstProjectCost)
min <- currency(min, digits = 0L)
if(is.nan(min)){min[is.nan(min)] <- 0}
if(is.infinite(min)){min[is.infinite(min)] <- 0}
max <- max(nbhd_pres$EstProjectCost)
max <- currency(max, digits = 0L)
if(is.nan(max)){max[is.nan(max)] <- 0}
if(is.infinite(max)){max[is.infinite(max)] <- 0}

#create bullet points
summary <- block_list(
  fpar(ftext(paste(params$month, params$year, "Neighborhood Cost Breakdown", sep = " "), reg24)),
  fpar(ftext(paste("Mean:", mean, sep = " "), reg24)),
  fpar(ftext(paste("Median:", median, sep = " "), reg24)),
  fpar(ftext(paste("Range:", min, "-", max, sep = " "), reg24))
)

#create powerpoint slide
report%>%
add_slide(layout = "Two Content")%>%
  ph_with(external_img(here::here("data", "neighborhood_pics", paste(abbr, ".png", sep = "")), height = 3.73, width = 4.19), location = ph_location_left(), use_loc_size = FALSE)%>%
 ph_with(summary, location = ph_location_right(), is_list = TRUE, level_list = c(1, 2, 2, 2))%>%
  ph_with(paste(neighborhood), 
               location = ph_location_type(
                 type = "title") )-> report
 
 #Summary stats
nbhd_past <- filter(lastmonth, nbhd_name == neighborhood)
tot_pres <- filter(ytd, nbhd_name == neighborhood)
tot_past <- filter(lastytd, nbhd_name == neighborhood)

#create cost and year to date variables for each year
bp_pres <- nrow(nbhd_pres)
bp_past <- nrow(nbhd_past)
cost_pres <- mean(nbhd_pres$EstProjectCost)
cost_pres <- currency(cost_pres, digits = 0L)
if(is.nan(cost_pres)){cost_pres[is.nan(cost_pres)] <- 0}
cost_past <- mean(nbhd_past$EstProjectCost)
cost_past <- currency(cost_past, digits = 0L)
if(is.nan(cost_past)){cost_past[is.nan(cost_past)] <- 0}
bptot_pres <- nrow(tot_pres)
bptot_past <- nrow(tot_past)
totcost_pres <- mean(tot_pres$EstProjectCost)
totcost_pres <- currency(totcost_pres, digits = 0L)
if(is.nan(totcost_pres)){totcost_pres[is.nan(totcost_pres)] <- 0}
totcost_past <- mean(tot_past$EstProjectCost)
totcost_past <- currency(totcost_past, digits = 0L)
if(is.nan(totcost_past)){totcost_past[is.nan(totcost_past)] <- 0}

#create percent change variables
pct_chg_cnt <- (bp_pres - bp_past)/bp_past
pct_chg_cnt <- percent(pct_chg_cnt)
if(is.nan(pct_chg_cnt)){pct_chg_cnt[is.nan(pct_chg_cnt)] <- 0}
if(is.infinite(pct_chg_cnt)){pct_chg_cnt[is.infinite(pct_chg_cnt)] <- "Infinite"}
pct_chg_cost <- (cost_pres - cost_past)/cost_past
pct_chg_cost <- percent(pct_chg_cost)
if(is.nan(pct_chg_cost)){pct_chg_cost[is.nan(pct_chg_cost)] <- 0}
if(is.infinite(pct_chg_cost)){pct_chg_cost[is.infinite(pct_chg_cost)] <- "Infinite"}
pct_chg_ytd <- (bptot_pres - bptot_past)/bptot_past
pct_chg_ytd <- percent(pct_chg_ytd)
if(is.nan(pct_chg_ytd)){pct_chg_ytd[is.nan(pct_chg_ytd)] <- 0}
if(is.infinite(pct_chg_ytd)){pct_chg_ytd[is.infinite(pct_chg_ytd)] <- "Infinite"}
pct_chg_cost_pres <- (totcost_pres - totcost_past)/totcost_past
pct_chg_cost_pres <- percent(pct_chg_cost_pres)
if(is.nan(pct_chg_cost_pres)){pct_chg_cost_pres[is.nan(pct_chg_cost_pres)] <- 0}
if(is.infinite(pct_chg_cost_pres)){pct_chg_cost_pres[is.infinite(pct_chg_cost_pres)] <- "Infinite"}
  
#create sprints for powerpoint output  
sprint_1 <- sprintf("%s building permits in %s %s",
                    bp_pres, params$month, params$year)
sprint_2 <- sprintf("%s total building permits in %s", 
                    bptot_pres, params$year)

# text formatting
color24a <- fp_text(color = ifelse(pct_chg_cnt == 0, "#00B0F0", ifelse(pct_chg_cnt > 0, "#00B050", "red")), font.size = 24)
color20a <- fp_text(color = ifelse(pct_chg_cost == 0, "#00B0F0", ifelse(pct_chg_cost > 0, "#00B050", "red")), font.size = 20)
color24b <- fp_text(color = ifelse(pct_chg_ytd == 0, '#00B0F0', ifelse(pct_chg_ytd > 0, '#00B050', 'red')), font.size = 24)
color20b <- fp_text(color = ifelse(pct_chg_cost_pres == 0, "#00B0F0", ifelse(pct_chg_cost_pres > 0, "#00B050", "red")), font.size = 20)
  

# create summary notes
summary <- block_list(
  fpar(ftext(sprint_1, boldline)),
  fpar(ftext(paste(pct_chg_cnt, "change ", sep = " "), color24a),
       ftext(paste("compared to ", params$month, " ", (params$year -1), " (", bp_past, " total building permits)", sep = ""), reg24)),
  fpar(ftext(paste(cost_pres), bold),
       ftext(paste(": Average building permit cost in", params$month, params$year, sep = " "), reg24)),
  fpar(ftext(paste(pct_chg_cost, "change", sep = " "), color20a),
       ftext(paste(" compared to ", params$month, " ", (params$year -1), " (", cost_past, ")", sep = ""), reg20)),
  fpar(ftext(sprint_2, boldline)),
  fpar(ftext(paste(pct_chg_ytd, "change ", sep = " "), color24b),
       ftext(paste("YTD compared to this time in ", (params$year -1), " (", bptot_past, " total building permits)", sep = ""), reg24)),
  fpar(ftext(paste(totcost_pres), bold),
       ftext(paste(": YTD average building permit cost in", params$year, sep = " "), reg24)),
  fpar(ftext(paste(pct_chg_cost_pres, "change", sep = " "), color20b),
       ftext(paste(" YTD compared to this time in ", (params$year -1), " (", totcost_past, ")", sep = ""), reg20))
)

# write summary notes to powerpoint slide
report%>%
  add_slide(layout = 'Title and Content', master = 'Office Theme')%>%
  ph_with(value = paste(neighborhood, ": Summary Notes", sep = ""), location = ph_location_type(type = "title"))%>%
  ph_with(summary, location = ph_location_type(type = "body"), is_list = TRUE, level_list = c(1, 2, 2, 3, 1, 2, 2, 3)) -> report

#Create color palette for mapping
col <- character(0)
if("Commercial" %in% nbhd_pres$new_use){col <- c("Commercial" = "#4daf4a")}
if("Industrial" %in% nbhd_pres$new_use){col <- c(col, "Industrial" = "#e41a1c")}
if("Residential" %in% nbhd_pres$new_use){col <- c(col, "Residential" = "#377eb8")}

#write shapefile
shp <- filter(merge, nbhd_name == neighborhood)
st_write(shp, here::here("data", params$year, params$month, "shapefiles", paste(abbr, ".shp", sep = "")), delete_dsn = TRUE)

#Load shapefile
st_read(here::here("data", params$year, params$month, "shapefiles", paste(abbr, ".shp", sep = "")),
        stringsAsFactors = FALSE) %>%
  st_transform(crs = 32615) -> nbhd_shp

#mapping
tm_shape(i) +
  tm_rgb() +
  nhoods_sf %>%
  filter(., neighborhood == num) %>%
  tm_shape() +
    tm_fill(col = "#9ecae1",
            alpha = .5) +
    tm_borders(col = "black",
               lwd = 2,
               lty = "dashed") +
  nbhd_shp%>%
  tm_shape() +
    tm_bubbles(size = .25,
               col = "new_use",
               palette = col,
               title.col = "Building Permit Type") +
  tm_credits("© Mapbox, © OpenStreetMap", position = c("left", "BOTTOM")) +
  tm_layout(
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom")) -> map

#save map as .jpeg
tmap_save(map, file = here::here("results", params$year, params$month, paste(abbr), paste(abbr, "_use.jpeg", sep = "")), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, paste(abbr), paste(abbr, "_use.jpeg", sep = "")), width = 9, height = 5), location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with(paste(neighborhood), 
               location = ph_location_type(
                 type = "title") )-> report

#create summary tables for current month and past 6 months
nbhd_pres%>%
  group_by(new_use)%>%
  summarize(mean = mean(EstProjectCost), count = n(), sum = sum(EstProjectCost))%>%
  dplyr::select(new_use, mean, count, sum) -> table

use[!(use %in% table$new_use)] -> missing_category
is_empty(missing_category) -> test

as.data.frame(table) -> table

if(test == FALSE) {
  add_row(table, new_use = missing_category) -> table
}
table%>%
  replace(., is.na(.), 0)%>%
  arrange(., new_use) -> table

  
month6%>%
  filter(nbhd_name == neighborhood)%>%
  group_by(new_use)%>%
  summarize(mean = mean(EstProjectCost), count = n(), sum = sum(EstProjectCost))%>%
  dplyr::select(new_use, mean, count, sum) -> table1

use[!(use %in% table1$new_use)] -> missing_category
is_empty(missing_category) -> test

as.data.frame(table1) -> table1

if(test == FALSE) {
  add_row(table1, new_use = missing_category) -> table1
}
table1%>%
  replace(., is.na(.), 0)%>%
  arrange(., new_use)  -> table1

#make summary tables
  flextable(table)%>%
  colformat_num(., digits = 0)%>%
  colformat_num(., digits = 0, prefix = "$", j = c(2,4)) %>%
  autofit()%>%
  add_header_lines(values = paste(params$month, params$year, sep = " "))%>%
  set_header_labels(new_use = "Permit Use", 
    mean = "Average Cost", count = "# of Permits", sum = "Total Value of Permits")%>%
    height_all(height = .5, part = "all")-> flex
  
  flextable(table1)%>%
  colformat_num(., digits = 0)%>%
  colformat_num(., digits = 0, prefix = "$", j = c(2,4)) %>%
  autofit()%>%
  add_header_lines(values = "Last 6 Months")%>%
  set_header_labels(new_use = "Permit Use", 
    mean = "Average Cost", count = "# of Permits", sum = "Total Value of Permits")%>%
    height_all(height = .5, part = "all") -> flex01

# add powerpoint slide
report%>%
  add_slide(layout = "Two Content")%>%
  ph_with(flex, location = ph_location_left())%>%
  ph_with(flex01, location = ph_location_right())%>%
  ph_with("Neighborhood Summary", 
               location = ph_location_type(
                 type = "title")) -> report

if(nrow(nbhd_pres) < 15){
    
    #create in depth summary table
  nbhd_pres%>%
    dplyr::select(OwnerName, new_use, EstProjectCost, OrigAddress) -> table
  
#make a currency value
table$EstProjectCost <- currency(table$EstProjectCost, digits = 0L)
  
#print summary table
  flextable(table)%>%
  colformat_num(., digits = 0, prefix = "$", j = 3) %>%
  autofit()%>%
  set_header_labels(OwnerName = "Owner", new_use = "New Use", 
    EstProjectCost = "Cost", OrigAddress = "address")%>%
    set_caption(paste(neighborhood, "Individual Permit Breakdown"))%>%
    height_all(height = .25, part = "all")-> flex02
  
#add powerpoint slide
  report%>%
    add_slide()%>%
    ph_with(value = paste(neighborhood, "Individual Permit Breakdown"), location = ph_location_type(type = "title"))%>%
    ph_with(flex02, location = ph_location_type(type = "body")) -> report
}

ggplot(nbhd_pres, aes(lrgcost)) +
  scale_colour_manual(
    values = cols,
    aesthetics = c("colour", "fill")
  ) +
  geom_bar(aes(fill = new_use), position = "dodge", stat="count") +
  theme(
    plot.title = element_text(hjust = 0.5),
  )+
  ylab("Number of Permits") +
  xlab("Building Permit Cost") +
  labs(fill = "New Use") -> plot

ggsave(here::here("results",  params$year, params$month, abbr, paste(abbr, "_cost.png", sep = "")), 
       plot = plot, width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, abbr, paste(abbr, "_cost.png", sep = "")),
                       width = 9, height = 5), location = ph_location_type(type = "body"),
                       use_loc_size = FALSE)%>%
  ph_with(value = paste(neighborhood, "Permit Cost Breakdown"), 
          location = ph_location_type(type = "title")) -> report
  }}

  # additional notes slide
report%>%
  add_slide()%>%
  ph_with(value = "Additional Notes", location = ph_location_type(type = "title"))%>%
  ph_with(c("Data retreived from https://www.stlouis-mo.gov/data/", "Building permits with a cost of $0 were dropped", "Building permits that were cancelled were dropped", "Infinite change indicates 0 permits in the current or previous time period/comparison month so there was a overall increase or decrease"), location = ph_location_type(type = "body")) -> report

# save powerpoint report
print(report, target = here::here("results", "presentations",  params$year, params$month, paste("bldgprmt_report", params$month, params$year, ".pptx", sep = "")))

#delete any existing permit report file
mydir <- paste("/Users/loganbogenut/Documents/GitHub/stl-building-permits/results/presentations/", params$year, "/", params$month, sep = "")
file.remove(file.path(mydir, dir(path = mydir, pattern = ".pdf")))

#convert & save powerpoint as PDF
convert_to_pdf(path = here::here("results", "presentations", params$year, params$month, paste("bldgprmt_report", params$month, params$year, ".pptx", sep = "")),
               pdf_file = sub("[.]pptx", ".pdf", paste("/Users/loganbogenut/Documents/GitHub/stl-building-permits/results/presentations/", params$year, "/", params$month, "/bldgprmt_report", params$month, params$year, ".pptx", sep = "")))

#Copy PDF to Shiny App
#delete any existing permit report file in the Shiny App
shinydr <- "/Users/loganbogenut/Documents/GitHub/crime_interactive/crime_interactive/www/"
file.remove(file.path(shinydr, dir(path = shinydr, pattern = "bldgprmt_report")))

file.copy(from=paste(mydir, "/bldgprmt_report", params$month, params$year, ".pdf", sep = ""), to=shinydr, 
          overwrite = TRUE, 
          copy.mode = TRUE)

# This code cleans our Global Environment and gives you a nice lil' message
rm(list = ls())
print("NICE JOB! You successfully ran all your code. Have an awesome day :)")
```

```{r, eval=FALSE}
library(stringr)
temp1 <- head(data_month,5)
#remove leading spaces and trailing spaces
owner <- dplyr::select(data_month, OwnerAddr)
orig <- dplyr:: select(data_month, OrigAddress)
owner$OwnerAddr <- gsub('^\\ |\\ $', '', owner$OwnerAddr)
orig$OrigAddress <- gsub('^\\ |\\ $', '', orig$OrigAddress)
#add space if number and letters are next to each other
owner$OwnerAddr <- gsub("([0-9])([A-Z])", "\\1 \\2", owner$OwnerAddr)
#split columns into address number and street name
orig_temp <- colsplit(data_month$OrigAddress, " ", c("num", "name"))
owner_temp <- colsplit(data_month$OwnerAddr, " ", c("num", "name"))
#combine columns
owner <- cbind(owner, owner_temp)
orig <- cbind(orig, orig_temp)
#drop leading and trailing spaces form name column
owner$name <- gsub('^\\ |\\ $', '', owner$name)
orig$name <- gsub('^\\ |\\ $', '', orig$name)
owner$num <- gsub("[^0-9.-]", "", owner$num) #remove all letters
owner$num <- sub("\\-.*", "", owner$num) #remove all dashes
owner$num <- gsub(" ", "", owner$num, fixed = TRUE) #remove all spaces
orig$num <- gsub("[^0-9.-]", "", orig$num) #remove all letters
orig$num <- sub("\\-.*", "", orig$num) #remove all dashes
orig$num <- gsub(" ", "", orig$num, fixed = TRUE) #remove all spaces
orig$num <- as.numeric(orig$num)
owner$num <- as.numeric(owner$num)
owner%>%
  mutate(similar = case_when(
    owner$num == orig$num ~ "Same",
    owner$num >= (orig$num-4) & owner$num <= (orig$num + 4) ~ "Similar",
    owner$num >= (orig$num-20) & owner$num <= (orig$num +20) ~ "Possible")) -> owner
#Remove directions of streets as well as suffixes
owner$name <- gsub('^\\N |\\ ST$', '', owner$name)
owner$name <- gsub('^\\S |\\ BLVD$', '', owner$name)
owner$name <- gsub('^\\E |\\ AV$', '', owner$name)
owner$name <- gsub('^\\W |\\ PL$', '', owner$name)
orig$name <- gsub('^\\N |\\ ST$', '', orig$name)
orig$name <- gsub('^\\S |\\ BLVD$', '', orig$name)
orig$name <- gsub('^\\E |\\ AV$', '', orig$name)
orig$name <- gsub('^\\W |\\ PL$', '', orig$name)
```

